A Road Segment Prioritization Approach for Cycling Infrastructure

### 2022-09-15 response to reviewers.Rmd

# Reviewer 1

*This paper presents an approach to help planners prioritize investments in cycling infrastructure.*

-   *Now that I have read the full article, I would consider this a methods paper, as it presents and describes a proposed method. This wasn't clear from the outset, and I found it difficult to follow without a clear methods and results section (there are methods and results presented, but I am not sure where they begin and end - they seem to be combined).*

We agree that this is a methods paper, and in fact focus on the **approach**​, which could be implemented using different methods.
The paper presents an implementation of the approach.
We have made this clear in the abstract and throughout (emphasis added to highlight the framing as a methods paper):

@@

"This paper demonstrates a new **approach** to support the prioritization of cycling infrastructure and cycling network design, accounting for cyclist preferences and the growing emphasis on 'filtered permeability' and 'Low Traffic Neighborhood' interventions internationally. The **approach** combines distance decay, route calculation, and network analysis methods to examine where future cycling demand is most likely to arise, how such demand could be accommodated within existing street networks, and how to ensure a fair distribution of investment. ***Although each of these methods has been applied to cycling infrastructure prioritization in previous research, this is the first time that they have been combined, creating an integrated road segment prioritization approach***."

We have updated the manuscript to make this clearer as suggested.
This has mostly been done in the Discussion and Conclusion section.
Furthermore, we have demonstrated applying the methods to additional locations in the appendix.

@@

-   *I see the merit of this paper, especially to policymakers, but I do wonder if the Journal of Transport Geography is the best fit for the paper. The contribution to geography is not especially clear. Perhaps Transport Policy, or some other policy-focused journal (or even a methods-focused journal) would be a better fit?*

The paper clearly fits the remit of Transport Geography well (based on the aims and scope of the journal, and previous papers in the area of geographic prioritisation of transport infrastructure and spatial inequalities in transport provision).
It presents a new methodological approach in planning cycling networks that is grounded in both GIS and literature on the impact of infrastructure on cycling uptake.

@@

-   *The inclusion of egalitarian principles in the paper was intriguing, but it was difficult to parse out exactly how this was done, how this approach differs from past work, and the implications/ benefits of using this approach.*

[How this approach differs from past work:]{.underline}

We are confident that the approach does different substantially from previous work in this area.
This is evidenced in the text below.

@@

end of section 2.2: "while these approaches deal with continuity better, they look at the network as a whole when attempting to improve it, and in doing so fail to account for equitable distribution of infrastructure"

section 2.3: "This research attempts to propose an egalitarian framework for cycling network design. This is done by identifying the different sub-networks that exist within the larger network, and ensuring that each gets a fair share of investment"

[How this was done/ benefits (bold is new text):]{.underline}

We have taken care to explain how this was done and the benefits, with reference to the literature.
We agree that the description of the benefits of the approach could have been made clearer and have taken steps in that direction.

@@

This paper presents an interesting approach to network design for cycling infrastructure.
I believe the proposed approach is really interesting and valid.

-   *However, the paper still has some flaws which should be solved. I suggest the authors to revise the structure of the paper: in particular, readers may not be familiar with the Manchester case. Instead it is taken for granted by the authors, who introduce the applied methodology in section 2 without ever having presented the case study and its peculiarities; even some results (e.g. those relating to the calculation of the demand potential) are presented in section 2, before having concluded the description of the methodology. Authors should choose from one of the following structures: 1) presentation of the different steps of the methodology (theoretically) and subsequent application to the case study. 2) Presentation of the case study and step-by-step application of the methodology, however including a clear schematization of it and any procedures to ensure its scalability.*

We have chosen option 2 as we think it is better to show the methodology and results for each subsection together.
Some context was added on Manchester and its recent cycling and walking targets (specifically the *Change a Region to Change a Nation* report [[link](https://beeactive.tfgm.com/publications-and-downloads/)].

We have created a methodology that is scalable and we have provided the code and instructions in a Github repository.
The instructions are in the README file in the R folder of the .zip file that accompanies this paper.
We have now clarified this and added a footnote that says "The results are easily reproducible for all UK cities, and can also be reproduced for cities elsewhere given the availability of commuter data. Instructions for reproducing the results are detailed in the **README** file in the R folder of this Github repository".
A link to the repo will be added after the paper is accepted.

### 2023-04-24 README.Rmd
peer review 2: flowchart and method headings

@@

<!-- EDIT! Add more to limitations -->

Our work builds on these community finding approaches by proposing a
similar greedy network expansion algorithm for cycle network expansion
*within communities*. We incorporate community finding methods for study
area partitioning with weighted routing to avoid links that are
stressful to cycle on. In doing so, we propose an approach that ensures a better distribution 
investments across the study area while also accounting for motivators and deterrents to cycling. 
We propose three sub-methods that address some of the limitations of previous
studies. These limitations include (a) an inherent bias when basing network
design solely on existing cycling demand, (b) the proposal of routes that may
not correspond to studies on cyclist preference and government policies,
and (c) an insufficient consideration of the ethical principles underlying
the analysis. The current work addresses these limitations through the following organisation. Section \@ref(calculating-potential-cycling-demand)
focuses on calculating potential cycling demand. Section \@ref(routing)
focuses on routing the demand onto the road network while accounting for
cyclist preferences and government priorities. Section
\@ref(road-segment-prioritization) outlines a method for partitioning the
study area based on a community finding algorithm and routed cycling
demand. It then introduces the network expansion algorithms, and compares an approach grounded in
'egalitarianism' to one grounded in 'utilitarianism'.

# Calculating Potential Cycling Demand

@@

# Routing

@@

# Road Segment Prioritization

@@

## Community Detection

@@

## Algorithm 1: Utilitarian Expansion

@@

## Algorithm 2: Egalitarian Expansion

@@

## Connectivity

>>>>

# Method and Application

## Method overview

@@

Our work builds on these community finding approaches by proposing a
similar greedy network expansion algorithm for cycle network expansion
*within communities*. We incorporate community finding methods for study
area partitioning with weighted routing to avoid links that are
stressful to cycle on. In doing so, we propose an approach that ensures a better distribution 
investments across the study area while also accounting for motivators and deterrents to cycling. 
We propose three sub-methods that address some of the limitations of previous
studies. These limitations include (a) an inherent bias when basing network
design solely on existing cycling demand, (b) the proposal of routes that may
not correspond to studies on cyclist preference and government policies,
and (c) an insufficient consideration of the ethical principles underlying
the analysis. The current work addresses these limitations through the following organisation. Section \@ref(calculating-potential-cycling-demand)
focuses on calculating potential cycling demand. Section \@ref(routing)
focuses on routing the demand onto the road network while accounting for
cyclist preferences and government priorities. Section
\@ref(road-segment-prioritization) outlines a method for partitioning the
study area based on a community finding algorithm and routed cycling
demand. It then introduces the network expansion algorithms, and compares an approach grounded in
'egalitarianism' to one grounded in 'utilitarianism'. As mentioned above, Manchester is used as a case study. 
An overview of the steps involved is shown in Figure \@ref(fig:methodflowchart).

```{r methodflowchart, fig.cap="Flowchart of proposed methodology", out.width="80%", fig.show='hold', fig.align = "center", echo=FALSE}
knitr::include_graphics("extras/methodology_flowchart.png")
```

## Calculating Potential Cycling Demand

@@

## Routing

@@

## Road Segment Prioritization

@@

### Community Detection

@@

### Algorithm 1: Utilitarian Expansion

@@

### Algorithm 2: Egalitarian Expansion

@@

### Connectivity
